Introducing statistics with \\texttt{intRo}

### 2014-12-05 student-paper-competition-2014/paper.Rmd
added flow chart for application creation

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{images/ui_annotate.png}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel. \ak{[Don't forget to update this.]}}
\label{fig:ui}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{images/ui_annotate.png}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{images/app_creation_modules.png}
\caption{This figure depicts how the \texttt{server.R} and \texttt{ui.R} files are populated using the modular structure within \texttt{intRo}.}
\label{fig:app_creation_modules}
\end{figure}

The process by which \texttt{intRo} is dynamically created upon running the application through module sourcing is detailed in figure~\ref{fig:app_creation_modules}. The key driver to populating \texttt{server.R} and \texttt{ui.R} is the file \texttt{modules.txt}, which defines the placement of each module. The interface is then created with the following statement.

\footnotesize
```{r ui, eval=FALSE}
## Source ui
module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")
sapply(file.path("modules", dir("modules")[dir("modules") != "modules.txt"], "ui.R"), source)

## Generates the UI tabs
mylist <- list()
old_heading <- ""
for (i in 1:nrow(module_info)) {
    if (module_info[i,1] != old_heading) {
        if (i != 1) mylist[[length(mylist) + 1]] <- "-----"
        mylist[[length(mylist) + 1]] <- as.character(module_info[i,1])
        old_heading <- module_info[i,1]
    }
    mylist[[length(mylist) + 1]] <- get(paste(module_info[i,2], "ui", sep = "_"))
}

## Create the UI
shinyUI(
    navbarPage("intRo", id="top-nav",  theme = "bootstrap.min.css",
               tabPanel(title="", icon=icon("home"),
                        fluidRow(
                            do.call(navlistPanel, c(list(id = "side-nav", widths = c(2, 10)), mylist))
                        )
               ), ...
    ))
```
\normalsize

The key piece of code being the `do.call` statement loading the list of ui elements from the module's \texttt{ui.R} file. The server functions are then dynamically generated using a similar method.

\footnotesize
```{r server, eval=FALSE}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")

  ## Modules
  types <- c("helper.R", "static.R", "observe.R", "reactive.R", "output.R")
  modules_tosource <- file.path("modules", apply(expand.grid(module_info$module, types), 1, paste, collapse = "/"))

  ## Source the modules
  for (mod in modules_tosource) {
      source(mod, local = TRUE)
  }
}
```
\normalsize
In this way, we were able to have \texttt{intRo} be fully extensible, its structure and functionality dependent entirely on the modules present within the application.
